Selective Sequential Model Selection

### 2015-11-01 paper.tex
a few more comments: computation of next-lambda tests, notation for log-likelihood

\subsubsection{Ever-Active Regularization Paths and next-$\lambda$ Tests}
Another important class of model selection procedures is the sequence of {\em ever-active} sets for a regularized likelihood path. 
The notion of ever-active sets is needed since these solution paths can drop  (as well as add) predictors along the way. 	For some ordered set $\Lambda$, let $\lambda\in\Lambda$ parameterize the regularization penalty $P_\lambda(\theta)$. In the case of lasso-penalized regression, we could take $P_\lambda = \lambda\|\beta\|_1$ for $\lambda\in (0,\infty]$. 
We assume $P_\lambda(\beta)$  has the property  that the model becomes less constrained as $\lambda$ decreases, that is,
 if $\lambda_2<\lambda_1$ then $\{\beta:P_{\lambda_2}(\beta)\} \supset \{\beta:P_{\lambda_1}(\beta)\}$.  \RTcomment{Will: is this correct?} \JTcomment{Yes, this looks a little funny to me too. Not all penalties produce
sparsity (for example, the generalized LASSO). So, I think this section is really thinking 
of $\ell_1$ norm (maybe a group LASSO norm). As written, 
we are also assuming that
there is a unique solution to (11) (which is not a big assumption but we might
as well make it.) Finally, $\ell$ does not actually have to be a likelihood.}

@@

@@

\subsubsection{Testing Against the Upper Model}
To avoid conditioning on the next model $M_k$, we could instead test $M_{k-1}$ against the alternative $M_{\infty}\setminus M_{k-1}$. In that case, we could modify~\eqref{eq:selModel_cond} and base the test on
\begin{equation}\label{eq:selModel_marg}
\L\left(X_{j_k}'Y \mid E_{k-1}, \; X_{E_{k-1}}'Y\right).
\end{equation}
We could also replace $X_{j_k}'Y$ with any other test statistic $T(Y)$. As long as $T(Y)$ is measurable with respect to $(M_k, U_k)$, and the path algorithm is subpath-sufficient, the $p$-values are guaranteed to be independent on nulls. The next-$\lambda$ test for the lasso and the max-$t$ test in forward-stepwise regression with unknown $\sigma^2$ are both examples of this approach. Note that under resampling from the law in~\eqref{eq:selModel_marg}, the selected variable $j_k$ is random; by contrast, \eqref{eq:selModel_cond} conditions on $j_k$.

@@

\JTcomment{Is there a reason you have $\psi$ and $\ell$ above instead of just $\ell$? I think the $(E,t)$ above should be $(E,u)$. It seems you never come back to $\psi$.}
\WFcomment{Fixed t/u. $\psi$ is the log-proportionality constant, I think we need it. Maybe I'm misunderstanding your question?}

>>>>

\subsubsection{Ever-Active Regularization Paths and next-$\lambda$ Tests}
Another important class of model selection procedures is the sequence of {\em ever-active} sets for a regularized likelihood path. 
The notion of ever-active sets is needed since these solution paths can drop  (as well as add) predictors along the way. 	For some ordered set $\Lambda$, let $\lambda\in\Lambda$ parameterize the regularization penalty $P_\lambda(\theta)$. In the case of lasso-penalized regression, we could take $P_\lambda = \lambda\|\beta\|_1$ for $\lambda\in (0,\infty]$. 
We assume $P_\lambda(\beta)$  has the property  that the model becomes less constrained as $\lambda$ decreases, that is,
 if $\lambda_2<\lambda_1$ then $\{\beta:P_{\lambda_2}(\beta)\} \supset \{\beta:P_{\lambda_1}(\beta)\}$.  \RTcomment{Will: is this correct?} \JTcomment{Yes, this looks a little funny to me too. Not all penalties produce
sparsity (for example, the generalized LASSO). So, I think this section is really thinking 
of $\ell_1$ norm (maybe a group LASSO norm). As written, 
we are also assuming that
there is a unique solution to (11) (which is not a big assumption but we might
as well make it.) Finally, $\ell$ does not actually have to be a likelihood.
BUT later on we implicitly assume that it is the likelihood for 
$M_{\infty}$. Why not just say this here, i.e. when talking
about $\ell_1$ regularization paths the models we have in mind are typically
going to be ones which correspond to a likelihood for some ``largest model'' for which we are trying to find a sub-model.

An example where we might not take $\ell$ to be a likelihood would be
if it were a pseudo-likelihood as in the neighborhood selection 
instead of graphical LASSO.
}

@@

\JTcomment{The next-$\lambda$ test is actually a little expensive to compute if we a finite set of $\lambda$  as, say, glmnet does. Should we not mention this? On the plus side, 
it gives us tests that do not require LAR and can be used with glmnet. 
Formally, to carry this out test, we need to draw samples of $Y$ conditioned
on the necessary sufficient statistics satisfying the necessary constraints 
(for LASSO, there $2(p-k)$ constraints on $X_{-E}^Ty$). Then, for each sample
we restart glmnet and run until the active set changes, storing this
value of $\lambda$. Then we compare our observed next-$\lambda$ to this
sample of $\lambda$'s.

In the LAR-LASSO case, this is easier as there is an explicit formula
to compute the next event. But, LAR is limited to LASSO whereas next-$\lambda$
in principle works for group LASSO.

Finally, the simplification of constraints we get really only works for
almost only for $\ell_1$. For group LASSO, the simplification
doesn't happen. The constraints after $k$ steps look like
$$
\left\{y: P_Ey=z, \|X_g^T(y - \hat{\mu}_l(z))\|_2 \leq \lambda_l \omega_g, 
g \in -E, 1 \leq l \leq k, \|(I-P_E)y\|=c\right\}
$$
where $z$ is the projection of our observed $y$ onto the ever active set.
So, for a given ``ever inactive group'', this says that $X_g^Ty$ is in
an intersection of $k$ balls which does not necessarily have a simple structure.
When all the groups are of size 1, i.e. in the LASSO, the intersection 
of $k$ balls is the intersection of $k$ intervals and we get a simplification.

All this to say, that we are really only talking about $\ell_1$ here, and 
next-$\lambda$ is essentially only practical BLAH
}

@@

\subsubsection{Testing Against the Upper Model}

To avoid conditioning on the next model $M_k$, we could instead test $M_{k-1}$ against the alternative $M_{\infty}\setminus M_{k-1}$. In that case, we could modify~\eqref{eq:selModel_cond} and base the test on
\begin{equation}\label{eq:selModel_marg}
\L\left(X_{j_k}'Y \mid E_{k-1}, \; X_{E_{k-1}}'Y\right).
\end{equation}
We could also replace $X_{j_k}'Y$ with any other test statistic $T(Y)$. As long as $T(Y)$ is measurable with respect to $(M_k, U_k)$, and the path algorithm is subpath-sufficient, the $p$-values are guaranteed to be independent on nulls. The next-$\lambda$ test for the lasso and the max-$t$ test in forward-stepwise regression with unknown $\sigma^2$ are both examples of this approach. Note that under resampling from the law in~\eqref{eq:selModel_marg}, the selected variable $j_k$ is random; by contrast, \eqref{eq:selModel_cond} conditions on $j_k$.

@@

\JTcomment{Is there a reason you have $\psi$ and $\ell$ above instead of just $\ell$? I think the $(E,t)$ above should be $(E,u)$. It seems you never come back to $\psi$.}
\WFcomment{Fixed t/u. $\psi$ is the log-proportionality constant, I think we need it. Maybe I'm misunderstanding your question?}
\JTcomment{I guess I meant that I am assuming that
$$
\ell(\theta) = \theta'U(y) - \psi(\theta)
$$
but I don't see how I would conclude that from what is written.
In principle, as written the $\psi$ above might be some other function but
(44) and (45) imply that the objective function is of the form
$$
\ell(\theta) = \tilde{\psi}(\theta) - \theta'U(y)
$$
for some $\tilde{\psi}$. In the proof when you say $\mathbb{E}_{\hat{\theta}^{\lambda}}[U_j]$ I am assuming this is $e_j^T\nabla \psi (\hat{\theta}^{\lambda})$ soshould I conclude that $\tilde{\psi}=\psi$?
}
